Rule Synthesis for Rule-based Intrusion Detectors

### 2020-06-02 paper/paper.tex
pass on abstract

\begin{abstract}
Network Intrusion Detection Systems (\nids{}) are popular tools to
defend against network attacks. These systems monitor the network
traffic and flag suspicious network behavior. Rule-based \nids\ do
that by checking the network traffic against a set of rules, which
become obsolete as attackers learn new strategies to circumvent
existing defenses. This paper proposes \tname{}, a novel approach to
synthesize rules for \textit{rule-based} \nids. \tname\ leverages
malicious (positive) and benign (negative) traffic 
%\rui{positive and negative traffic are first introduced here, withuot being explaiend.} 
and examples of trusted rules to create
rules for new attacks. \tname{} is organized as a pipeline of three components that
1)~create an over-specified seed rule, 2)~derive plausible rules from
the seed, and 3)~rank plausible rules. Experimental results provide
evidence that \tname\ is promising.
 \rui{the example is interesting, but this gives the 
feeling that the work is too preliminary} 
For example, it was
able to synthesize the correct rule in all cases we analyzed and
ranked the correct rule among the first ten rules of the reported
ranking in \percTopFiveRanking\ of the cases.
\end{abstract}

>>>>

% and examples of trusted rules

\begin{abstract}
Network Intrusion Detection Systems (\nids{}) are popular tools to
defend local networks against attacks. These systems monitor the
network traffic and flag suspicious behavior. Rule-based \nids\ do
that by checking the network traffic against a set of rules, which
become obsolete as attackers learn new strategies to circumvent
existing defenses. This paper proposes \tname{}, a novel approach to
synthesize rules for rule-based \nids. \tname\ leverages malicious
(positive) and benign (negative) traffic to create rules for new
attacks. \tname{} is organized as a pipeline of three components to
1)~create an over-specified seed rule, 2)~derive plausible rules from
the seed, and 3)~rank plausible rules. We evaluated \tname\ against a
set of 21 network attacks with varios
characteristics. \tname\ performed very well, being capable of
generating the correct rule among the top-3 and top-1 rules of the
ranking, respectively, in \percTopThreeRankingPrefix\ and
\percTopOneRankingPrefix\ of the cases.
\end{abstract}
